Extended Early Adulthood and Attitude Change

### 2024-07-11 manuscript/manuscript.Rmd
updated analysis and table

| Col1             | Col2  | Col3 | Col4 |
|------------------|-------|------|------|
| Fixed Effects    |       |      |      |
| Intercept        | 17.45 |      |      |
| Time (decade)    | -0.26 |      |      |
| Age(26-33)       | -1.60 |      |      |
| Age(34-64)       | -3.17 |      |      |
| Age(65+)         | -4.10 |      |      |
| Duration (year)  | 1.13  |      |      |
| Time\*Age(26-33) | -0.09 |      |      |
| Time\*Age(34-64) | -0.54 |      |      |
| Time\*Age(65+)   | -1.33 |      |      |
|                  |       |      |      |
| Random Effects   | S.D.  |      |      |
| Intercept        | 5.35  |      |      |
| Time             | 1.14  |      |      |
| Duration         | 0.37  |      |      |
| Age(26-33)       | 0.89  |      |      |
| Age(34-64)       | 1.81  |      |      |
| Age(64+)         | 2.92  |      |      |

: Coefficient Estimates

>>>>

|                          | Model 1       | Model 2      |
|--------------------------|---------------|--------------|
| **Fixed Effects**        |               |              |
|  Intercept               | 17.77 (0.75)  | 17.46 (0.77) |
|  Time (decade)           | -0.01 (0.17)  | -0.15 (0.17) |
|  Age(26-33)              | -0.94 (0.35)  | 0.42 (0.35)  |
|  Age(34-64)              | -2.49 (0.37)  | -0.82 (0.36) |
|  Age(65+)                | -3.39 (0.48)  | -1.70 (0.44) |
|  Duration (year)         | 1.45 (0.10)   | 1.56 (0.10)  |
|  Time\*Age(26-33)        | -0.02 (0.07)  | 0.18 (0.07)  |
|  Time\*Age(34-64)        | -0.51 (0.06)  | -0.15 (0.06) |
|  Time\*Age(65+)          | -1.38 (0.07)  | -0.80 (0.07) |
| Duration\*Age(26-33)     | -0.17 (0.09)  | -0.28 (0.08) |
| Duration\*Age(34-64)     | -0.38 (0.08)  | -0.49 (0.07) |
| Duration\*Age(65+)       | -0.51 (0.02)  | -0.58 (0.09) |
| Duration\*Time           | 0.14 (0.02)   | 0.15 (0.02)  |
| Ever married             |               | -0.89 (0.21) |
| Ever had child           |               | 0.26 (0.14)  |
| Child under 18 in house  |               | 0.30 (0.10)  |
| Student                  |               | -0.57 (0.24) |
| Less than HS             |               | 2.80 (0.35)  |
| College degree           |               | -2.42 (0.24) |
|                          |               |              |
| **Random Effects**       | **S.D.**      | **S.D.**     |
|  Intercept               | 5.99          | 6.24         |
|  Time                    | 1.32          | 1.31         |
|  Duration                | 0.50          | 0.50         |
|  Age(26-33)              | 1.42          | 1.32         |
|  Age(34-64)              | 2.26          | 1.99         |
|  Age(64+)                | 3.06          | 2.41         |
|  Ever married            |               | 1.60         |
|  Ever had child          |               | 0.88         |
|  Child under 18 in house |               | 0.67         |
|  Student                 |               | 1.72         |
|  Less than HS            |               | 1.04         |
|  College degree          |               | 2.98         |

: Table \@ref(tab:2): Coefficient estimates from multilevel linear regressions of absolute change between responses on age group, duration, and question.
